\section{Introduction}
\label{sec:introduction}

Video game quality assurance is a labor-intensive process in which testers search for visual
and behavioral anomalies across hours of gameplay footage. Glitches --- unintended deviations
from expected game behavior --- range from geometry clipping and texture corruption to frozen
animations and physics violations. Detecting these anomalies automatically is valuable both
during development and for post-release monitoring, yet the task is difficult: glitches can be
subtle, game-specific, and sometimes visible only across a sequence of frames rather than in any
single image~\cite{tempglitch,worldofbugs}.

Existing automated approaches to game glitch detection fall into two broad families. The first
relies on large pretrained vision-language models (VLMs) queried at test time with image or
video prompts~\cite{glitchbench,tempglitch}. These models are general-purpose and require no
game-specific training, but they remain near chance on temporal glitch benchmarks~\cite{tempglitch}
and are expensive to query at scale. The second family uses curated classification datasets with
explicit positive and negative labels, which requires collecting labeled glitch examples for each
game or glitch type~\cite{worldofbugs}.

We explore a complementary direction. Rather than using a large VLM or a labeled glitch
dataset, we ask whether the \emph{latent prediction error} of a compact world model trained
exclusively on normal gameplay can serve as a label-free signal for episode-level glitch
detection. The intuition is straightforward: a world model that has learned the latent dynamics
of normal play should produce larger prediction errors when it encounters abnormal transitions,
such as those produced by glitches. This idea has clear precedent in the world-model
literature~\cite{worldmodels,dreamerv3}, but has not been evaluated in the game-glitch domain
with explicit leakage-aware episodic splits.

We instantiate this approach as \textbf{LeWM-Glitch}, using the frozen checkpoints of
LeWorldModel~\cite{lewm} --- a JEPA-style end-to-end pixel-conditioned dynamics model ---
as a fixed feature extractor. Figure~\ref{fig:pipeline} summarizes the scoring pipeline.
The method requires no glitch labels during training or calibration; the only labeled
information it uses is the identity of normal episodes for threshold calibration. We evaluate
LeWM-Glitch under a strict leakage-aware protocol that enforces source-, pair-, and
episode-disjoint role separation before window generation.

This paper makes the following contributions:
\begin{enumerate}
  \item We formulate episode-level gameplay glitch detection as latent prediction error scoring
  over a normal-trained JEPA world model and define a clean leakage-aware evaluation protocol
  with three disjoint roles: train-normal, calibration-normal, and evaluation.
  \item We report bounded evaluation results on two independently frozen, non-locked splits:
  a TempGlitch-based follow-up (12 normal, 22 buggy episodes) and a secondary R5-XGame split
  (12 normal, 60 buggy episodes), including bootstrap confidence intervals.
  \item We report honest negative findings on GlitchBench (K2) and a mechanistic ablation (K3),
  showing that the positive results are not explained by SIGReg regularization or
  real-action conditioning, and that LeWM-Glitch does not transfer to image-level glitch detection.
  \item We provide a reproducible, artifact-backed experiment package with SHA-256 provenance,
  a validator-backed claim registry, and a non-locked validation boundary that is clearly
  distinguished from any future locked-test evaluation.
\end{enumerate}

All results are non-locked validation evidence on small, frozen splits.
We make no claims of statistical superiority, broad generalization, temporal localization,
or deployment readiness.
