\section{Related Work}
\label{sec:related-work}

\paragraph{Game glitch detection.}
Automated detection of visual bugs and glitches in games is an emerging research challenge.
GlitchBench introduced a standardized benchmark asking whether large multimodal models can
identify glitches from static screenshots~\cite{glitchbench}. World of Bugs (WOB) provided an
earlier controlled platform for programmatic 3D bug injection and automated oracle
evaluation~\cite{worldofbugs}. TempGlitch shifted the focus to temporal gameplay sequences,
evaluating vision-language models on videos where glitch evidence spans multiple frames rather
than a single image~\cite{tempglitch}. VideoGlitchBench extended this to video-level
detection across multiple game families with explicit leakage-aware splits~\cite{videoglitchbench}.
RESP proposed a retrieval-augmented spatial prediction baseline for glitch scoring~\cite{resp},
while PhysGame examined physical commonsense violations in gameplay as a related failure
mode~\cite{physgame}. Our work differs from all of these: rather than using large pretrained
vision-language models or retrieval augmentation, we train a compact JEPA world model on
normal gameplay and exploit its latent prediction error directly as a label-free signal.

\paragraph{Video anomaly detection.}
Video anomaly detection commonly models the distribution of normal behavior and raises an alert
when observations deviate. Weakly supervised approaches such as UCF-Crime~\cite{sultani2018ucfcrime}
and memory-guided normality modeling~\cite{park2020mnad} have advanced the field on surveillance
benchmarks. More recently, FrameShield~\cite{frameshield} demonstrated contrastive frame-level
shielding for temporal anomaly detection at NeurIPS 2025. Score-based
out-of-distribution work~\cite{hendrycks2017baseline,guo2017calibration} motivates the use of
scalar surprise signals but does not address the domain-specific challenge of game glitch
semantics or the leakage risks inherent in episode-derived splits. Our method adopts the
normal-only training paradigm but applies it to latent representation space via a world model
rather than pixel reconstruction.
TempGlitch~\cite{tempglitch} further reports that current vision-language models remain near
chance on temporal gameplay glitch sequences, motivating compact episode-level surprise signals
that do not require prompting a large VLM at test time.

\paragraph{World models and latent dynamics.}
Ha and Schmidhuber's World Models established the idea of compressing environment observations
into a learned latent dynamics model~\cite{worldmodels}. PlaNet extended this with a
recurrent state-space model for planning from pixels~\cite{planet}, and DreamerV3 pushed
this lineage to diverse game domains with robust latent prediction~\cite{dreamerv3}. These
models learn to predict future latent states; large prediction error signals an unexpected
transition. LeWM-Glitch directly inherits this intuition, using the latent prediction error
of LeWorldModel~\cite{lewm} --- a stable end-to-end JEPA trained on gameplay pixels --- as
its anomaly score.

\paragraph{JEPA family.}
Joint-Embedding Predictive Architectures (JEPA) predict representations of target observations
from context representations rather than predicting raw pixels, making the representation
space the locus of prediction~\cite{ijepa}. V-JEPA extended this to video by predicting
masked spatiotemporal regions~\cite{vjepa}, and V-JEPA~2 further improved planning and
prediction capabilities~\cite{vjepa2}. LeWorldModel~\cite{lewm} adapts the JEPA paradigm to
an end-to-end pixel-conditioned dynamics model with AdaLN conditioning and SIGReg
regularization; we use its frozen checkpoints as the backbone of LeWM-Glitch.

\paragraph{Research gap.}
Prior game glitch detection work has relied on large VLMs queried at test time, retrieval
augmentation, or classification probes on curated image datasets. This paper explores a
complementary direction: training or reusing a compact JEPA latent world model on normal
gameplay and exploiting its prediction error as a label-free detection signal across multiple
temporal benchmarks with explicit leakage control. LeWM-Glitch fills this gap by providing a
JEPA-LPE-based glitch detector with a reproducible, artifact-bound evaluation protocol.

Table~\ref{tab:literature-matrix} records what each literature group supports and, equally
importantly, what it does not support for this paper.

\paragraph{Concurrent work.}
Two concurrent preprints are relevant. RESP~\cite{resp} proposes a retrieval-enhanced spatial
prediction baseline for video game glitch scoring, operating at the frame level without a
world-model prior. T-SAR-JEPA~\cite{tsarjepa2026} applies JEPA-style anomaly detection to
synthetic-aperture radar imagery, demonstrating that JEPA prediction error can be studied outside
natural video; however, it does not address temporal game dynamics. LeWM-Glitch differs from both
by using a compact JEPA world model trained on normal gameplay to produce a label-free
episode-level surprise signal under strict leakage-aware evaluation.

\input{tables/literature_matrix}
