\section{Problem Formulation}
\label{sec:problem}

\subsection{Episodes, Windows, and Roles}

Let a gameplay \emph{episode} $e$ be a contiguous sequence of video frames
$\mathbf{x}_e = (x_1, x_2, \ldots, x_T)$ recorded during a single play session.
We say episode $e$ is \emph{normal} if it was recorded without any programmatic bug injection
and \emph{buggy-positive} otherwise.
All episodes are partitioned into three non-overlapping roles before any window is generated:
\begin{itemize}
  \item $\mathcal{E}_{\text{train}}$: normal episodes used to fit any train-dependent model
  component (in our setting, none beyond the pretrained LeWM checkpoint).
  \item $\mathcal{E}_{\text{cal}}$: normal episodes used only to set the detection threshold;
  no metric from these episodes is reported.
  \item $\mathcal{E}_{\text{eval}}$: held-out episodes (normal-negative and buggy-positive)
  used to compute all reported metrics.
\end{itemize}
Role assignment is performed at the \emph{source} and \emph{pair} level before episode
enumeration, so no source or pair straddles two roles.

\subsection{Window Scoring}

Each episode is divided into non-overlapping windows of $w$ consecutive frames.
Let $f_\theta$ denote the frozen LeWorldModel encoder and $g_\phi$ the frozen JEPA predictor.
For window $t$ in episode $e$, the window-level \emph{latent prediction error} (LPE) is:
\begin{equation}
  d_{e,t} = \bigl\| g_\phi(f_\theta(x_t)) - f_\theta(x_{t+1}) \bigr\|_2^2
  \label{eq:lpe}
\end{equation}
where $x_t$ and $x_{t+1}$ are the anchor and target frames of the window.
All model parameters are frozen at the pretrained LeWM checkpoint; no fine-tuning is performed.

\subsection{Episode Aggregation}

Window-level scores are aggregated to a scalar episode score:
\begin{equation}
  S_e = A\bigl(\{d_{e,t}\}_{t=1}^{N_e}\bigr)
  \label{eq:aggregation}
\end{equation}
where $A$ is an aggregation function. We evaluate several options including \texttt{mean},
\texttt{max}, and \texttt{top2\_mean} (mean of the top-2 scoring windows).
The choice of $A$ is treated as a configuration dimension; results are reported per
configuration without post-hoc selection on evaluation data.

\subsection{Calibration and Decision Rule}

The detection threshold $\tau$ is computed from the calibration-normal episodes only:
\begin{equation}
  \tau = \text{percentile}_{q}\bigl(\{S_e\}_{e \in \mathcal{E}_{\text{cal}}}\bigr)
  \label{eq:threshold}
\end{equation}
where $q$ is a fixed quantile (e.g., 95th percentile) chosen before evaluation.
An episode is classified as anomalous if $S_e \geq \tau$; otherwise it is classified as normal:
\begin{equation}
  \hat{y}_e = \mathbf{1}[S_e \geq \tau]
  \label{eq:decision}
\end{equation}

Window scores $d_{e,t}$ are used for diagnostic visualization only.
We do not assign temporal span labels to windows and do not evaluate temporal localization
metrics, because no verified temporal span ground truth exists in the current benchmark splits.
