\section{Experimental Setup}
\label{sec:experiments}

The paper now integrates five validated evidence lanes plus one secondary family, each with its
own claim boundary.

\paragraph{Main TempGlitch follow-up.}
Artifact-backed LeWM checkpoints from seeds 42, 43, and 44 are scored with six latent-surprise
window scorers and three episode aggregations, producing 54 LeWM rows. The two simple baselines,
\texttt{frame\_diff} and \texttt{feature\_distance}, are each combined with the same three episode
aggregations, producing six baseline rows. The headline comparison reports the highest recorded
AUROC row within each family on the exact same frozen support; it does not retrain a model or
refit a threshold after looking at evaluation outcomes.

\paragraph{K1 exact-support learned baselines.}
Three learned video baselines are scored on the same TempGlitch follow-up support used by the main
table. Each learned baseline is reported across \texttt{mean}, \texttt{max}, and
\texttt{top2\_mean} episode aggregation, producing nine rows. Paper tables retain only the best
aggregation per learned method plus the paired comparison against the best LeWM row.

\paragraph{K2 bounded GlitchBench benchmark.}
The current executable GlitchBench path is a bounded image-level synthetic-normal split with 12
train-normal clips and 24 validation clips. The K2 table reports the validated simple,
learned-baseline, and LeWM rows produced by that exact package. Because the package is image-level
and uses synthetic normal counterparts, K2 is treated as a bounded public-benchmark surface, not
as a final gameplay QA benchmark.

\paragraph{K3 mechanistic ablation.}
The K3 artifact contains 12 controlled validation-normal training variants: SIGReg on/off crossed
with real-action/zero-action mode for seeds 42, 43, and 44. K3 is read out through the best total
validation loss and the minimum recorded prediction-loss diagnostic. It is a mechanistic training
objective comparison only; no detection AUROC, locked-test, or superiority claim follows from it.

\paragraph{Qualitative timeline lane.}
The repository preserves window-level LeWM score series and now provides a validated qualitative
timeline generator. The current receipt produces one representative buggy trajectory for the
best-by-AUROC TempGlitch LeWM configuration, but the artifact boundary explicitly states
\texttt{temporal\_metrics\_claimed = false}. The figure is therefore illustrative and does not
count as temporal localization.

\paragraph{Secondary R5-XGame evidence.}
R5-XGame retains the same 60-row configuration structure on its own frozen 72-episode evaluation
support. Its best recorded rows are presented as separate secondary evidence. Descriptive seed,
scorer, and aggregation summaries from that bundle remain exploratory, and the family is not used
to support cross-game generalization.

The earlier one-buggy-episode pilot, exposed sequential-subset results, and rows scored on
different manifests remain excluded from the main paper tables.
