\section{Bounded Results}
\label{sec:results}

TODO: keep this section limited to validated, hash-addressable result families. Do not add
ablation, WOB, locked-test, or cross-dataset result prose without a corresponding validated
artifact and claim-registry update.

Table~\ref{tab:r5-bounded-results} summarizes the current qualified comparison surface. The table
caption explicitly states the permitted scope: \emph{Non-locked TempGlitch validation-only
identical-episode family.}

\input{tables/r5_bounded_results}

Within this frozen family, the best observed AUROC and AUPRC rows came from seed44 LeWM variants,
while a \texttt{frame\_diff} configuration produced the strongest bounded F1 row. These are exact
family-qualified observations, not broad method claims. The confidence intervals are wide enough to
reinforce that this paper should emphasize provenance and containment over triumphal framing.

The safe interpretation is therefore modest: the repository now contains a full provenance-bound
R5 evaluation bundle and a reproducible bounded comparison table. The unsafe interpretation would
be to promote these rows into a general claim of superiority, state of the art, or cross-dataset
readiness. Appendix~\ref{app:forbidden-claims} makes that distinction explicit.

\subsection{World of Bugs Results (Positive-Probe Only)}
\label{sec:results-wob}

% PLACEHOLDER -- do not promote the validated positive-probe bundle into a
% binary-benchmark table.
Table~\ref{tab:r5-wob-results} remains a placeholder because the validated \texttt{R5-WOB} bundle is a
positive-probe result family with zero held-out normal-negative evaluation episodes. It supports
pipeline-execution and signal-presence discussion only, not a binary-detection performance claim.

\input{tables/r5_wob_results}

\subsection{Cross-Dataset Comparison (Pending)}
\label{sec:results-xgame}

% PLACEHOLDER -- do not insert cross-dataset numbers until a separately
% validated comparison artifact exists.
Table~\ref{tab:r5-xgame-results} remains reserved for a future cross-dataset comparison between
TempGlitch and World of Bugs under matched reporting discipline. The repo now has a validated
non-locked \texttt{R5-XGame} binary bundle, but the current \texttt{R5-WOB} evidence is still positive-probe
only and no separate cross-dataset comparison artifact has been validated. No cross-game
generalization claim is supported.

\input{tables/r5_xgame_results}

\subsection{Ablation Results (Pending)}
\label{sec:results-ablation}

% PLACEHOLDER -- do not insert ablation numbers until R6 ablations complete.
Table~\ref{tab:r6-ablation-results} is reserved for the R6 minimal decision-relevant ablation
study. No SIGReg benefit, action-conditioning benefit, or aggregation-superiority claim is
supported until the corresponding ablation outputs exist and are validated.

\input{tables/r6_ablation_results}
