\section{Results}
\label{sec:results}

\subsection{Primary Result 1: TempGlitch Pair-Disjoint Follow-up}

Table~\ref{tab:r5-bounded-results} reports the frozen pair-disjoint, non-locked, same-support
TempGlitch comparison. Every row uses 12 normal-negative and 22 buggy-positive evaluation
episodes after calibration on two normal episodes; source, pair, and episode overlap across roles
is zero.

\input{tables/r5_bounded_results}

The best recorded LeWM-Glitch row is seed44 \texttt{lewm\_l2\_max} with mean episode aggregation.
It reaches AUROC 0.7159, AUPRC 0.8026, F1 0.7143, precision 0.7500, recall 0.6818, balanced
accuracy 0.6326, and FPR@95TPR 0.7500 with AUROC 95\% CI [0.5349, 0.8770]. The strongest simple
baseline by AUROC is \texttt{feature\_distance} with \texttt{top2\_mean} aggregation at
AUROC 0.6136 and AUPRC 0.7310. Within this exact frozen support, the best LeWM-Glitch row shows
stronger observed same-support separation than the simple baselines, but the AUROC intervals
overlap and the operating-point false-positive rate remains high.

\subsection{Exact-Support Learned Baselines (TempGlitch)}

Table~\ref{tab:k1-learned-baselines} extends the same TempGlitch follow-up support with three
learned video baselines.

\input{tables/k1_learned_baselines}

The strongest learned baseline is \texttt{cnn\_lstm} with \texttt{max} episode aggregation, at
AUROC 0.6136, AUPRC 0.7249, and F1 0.7111. Its AUROC numerically matches the strongest simple
baseline and remains below the best LeWM-Glitch row. The paired delta-AUROC versus the best
LeWM-Glitch row is $-0.1023$ with 95\% bootstrap interval $[-0.2425,\ 0.0372]$ and
DeLong $p=0.2091$, so the evidence supports only bounded stronger-observed-separation wording
for LeWM-Glitch rather than a significant superiority claim.
The VideoMAE-small feature-distance baseline is included as a transformer-based learned
comparison; on this support it remains below the best LeWM-Glitch row, but this single bounded
result is not sufficient to isolate a JEPA-specific advantage from training budget, support size,
or scoring design.

\paragraph{Comparison with VLM baselines on TempGlitch.}
The TempGlitch benchmark reports that current vision-language models remain near chance on
temporal glitch sequences~\cite{tempglitch}. The best LeWM-Glitch configuration on our frozen
pair-disjoint follow-up reaches AUROC 0.7159, providing stronger observed separation than those
reported VLM behaviors on the temporal binary task. This comparison is contextual rather than
same-split: the exact evaluation episodes and prompting protocols differ, and the claim does not
extend to static screenshot tasks where VLMs and image-level classifiers may be stronger.

\subsection{Secondary R5-XGame Frozen Evaluation}

Table~\ref{tab:r5-xgame-results} reports the frozen non-locked R5-XGame family. This is a
secondary bounded result alongside TempGlitch, evaluated on a different game distribution with a
larger buggy-positive class (12 normal-negative, 60 buggy-positive episodes).

\input{tables/r5_xgame_results}

The best recorded LeWM-Glitch row (seed44 \texttt{lewm\_mse\_max} + \texttt{top2\_mean})
achieves AUROC 0.9097, AUPRC 0.9814, F1 0.7921, precision 0.9756, recall 0.6667,
balanced accuracy 0.7917, and FPR@95TPR 0.4167, with AUROC 95\% CI [0.8281, 0.9720].
Simple baselines reach AUROC 0.7681 (\texttt{feature\_distance}) and 0.7167
(\texttt{frame\_difference}).
On this split, the best LeWM-Glitch AUROC is numerically above the best baseline AUROC, but the
AUROC confidence intervals still overlap ([0.8281, 0.9720] versus [0.6484, 0.8719]); this
supports bounded stronger observed separation, not significant superiority.

These values are not directly compared with TempGlitch values. The two result families differ
in dataset distribution, class balance, calibration support, action mode, and training lineage.
The R5-XGame result is evidence about its own frozen split; it does not establish cross-game
generalization.

\subsection{Bounded GlitchBench K2 Benchmark (Honest Negative)}

Table~\ref{tab:glitchbench-benchmark} reports the validated K2 GlitchBench slice. This is an
honest negative result that we report as a community-value finding.

\input{tables/glitchbench_benchmark}

On this image-level synthetic-normal split (24 validation examples),
\texttt{feature\_distance}, \texttt{video\_autoencoder}, \texttt{cnn\_lstm}, and
\texttt{video\_transformer} each reach AUROC 1.0 and AUPRC 1.0, while the best recorded
LeWM-Glitch row reaches AUROC 0.5. This is an expected architectural mismatch rather than a
hidden positive result: GlitchBench K2 presents static image-level evidence, while LeWM-Glitch
derives its signal from temporal latent prediction error. The non-LeWM AUROC-1.0 rows still share
F1 0.6667 and balanced accuracy 0.5 under the shared train-normal \texttt{p95} threshold rule,
highlighting the distinction between ranking quality and threshold calibration. K2 therefore acts
as an honest negative comparison surface: the current method captures temporal surprise, not a
generic static visual-glitch prior.

\subsection{K3 Mechanistic Ablation (Honest Negative)}

Table~\ref{tab:k3-ablation-results} summarizes the controlled K3 validation-normal readout.
This is an honest negative mechanistic finding reported as a community-value contribution.

\input{tables/k3_ablation_results}

Across the six matched SIGReg-on versus SIGReg-off comparisons, the lower-is-better prediction
loss never improves when SIGReg is enabled. Real-action versus zero-action prediction-loss
deltas are also not directionally stable across seeds. This is an honest negative mechanistic
readout for the specific K3 training objective; it does not invalidate the detection-performance
results above, but it does indicate that the SIGReg and action-conditioning components of
LeWM do not provide measurable benefits at this scale and configuration.

\subsection{Qualitative Surprise Timelines}

The qualitative timeline lane is summarized in Table~\ref{tab:qualitative-timelines}.

\input{tables/qualitative_timeline_summary}

These figures show that the best validated TempGlitch LeWM-Glitch configuration yields
interpretable within-episode score trajectories. However, the current artifacts do not expose
real temporal span labels. The timelines therefore remain qualitative illustrations only and do
not support temporal IoU, temporal AP, onset, offset, or duration claims. Temporal localization
is future work.
