\section{Discussion}
\label{sec:discussion}

\paragraph{Why pair-disjoint calibration matters.}
The TempGlitch follow-up improves on the earlier identical-episode family by preventing the
calibration normals from sharing source, suspected pair, or episode identity with evaluation
episodes. This matters because paired normal and buggy captures may share scene layout, assets,
camera motion, or recording conditions. A threshold calibrated on a related normal could encode
pair-specific information rather than a transferable notion of normality. The repaired split does
not eliminate every possible dataset bias, but it closes the documented cross-role overlap and
makes the learned-baseline comparison materially more interpretable.

\paragraph{What the exact-support comparison says.}
The best recorded LeWM row remains the strongest observed TempGlitch row once learned baselines are
added on the same support, but the strength of that observation is limited. The strongest
learned-baseline AUROC delta crosses zero, the calibration support remains only two episodes, the
negative support remains 12 episodes, and FPR@95TPR is still 0.7500. The scientifically useful
conclusion is that latent surprise remains competitive on this split and merits further controlled
study, not that it has won a benchmark generally.

\paragraph{What K-A expanded adds.}
The expanded TempGlitch follow-up addresses one obvious weakness of the original support by
raising the evaluation set from 34 to 67 episodes while preserving the same non-locked,
pair-disjoint safety boundary. Its best LeWM row again records higher observed AUROC than the best
simple baseline, but the effect remains moderate and uncertainty remains visible. We therefore use
K-A expanded as robustness evidence for the method story, not as a new headline claim.

\paragraph{Why the negative evidence matters.}
K2 and K3 strengthen the paper precisely because they are not uniformly favorable to LeWM. K2 is a
bounded public-benchmark slice on which the current LeWM rows trail the validated simple and
learned-baseline top rows. K3 is a controlled mechanistic readout on which neither SIGReg nor
real-action conditioning shows a positive directional pattern. Keeping those negative findings in
the paper makes the method story more honest and more useful than a selective positive report.

\paragraph{Why qualitative timelines are still worthwhile.}
Even without span labels, window-level surprise plots remain helpful for diagnosing whether a high
episode score comes from a single peak, a sustained elevation, or a noisy trajectory. That is a
useful interpretability aid for a method paper. The boundary remains clear: these plots do not
convert the study into a temporal-localization benchmark.

\paragraph{Why the evidence surfaces stay separate.}
R5-XGame and R5-WOB still serve different purposes from TempGlitch. R5-XGame provides a secondary
positive-heavy binary family with real-action evidence, while R5-WOB remains positive-probe only.
Their role in this manuscript is to broaden the empirical picture without erasing protocol
differences or implying cross-game generalization.

\subsection{How the Positive and Negative Results Fit One Method Story}

The TempGlitch, R5-XGame, and K2 results are consistent with the method's intended temporal
scope. TempGlitch and R5-XGame contain episode-level evidence, while GlitchBench K2 is an
image-level slice constructed from static visual evidence. This contrast does not prove that
temporal dynamics cause the positive results, but it gives a useful interpretation of the
evidence boundary: LeWM-Glitch should be treated as an episode-level latent-surprise scorer, not
as a generic screenshot glitch classifier.
In short, TempGlitch supports the same-support pair-disjoint comparison, K-A expanded checks that
the TempGlitch observation is not limited to the smallest support, R5-XGame supports only its own
positive-heavy split, K2 and K3 remain honest negative evidence, and the qualitative timeline is a
diagnostic plot rather than a localization result.
