\section{Reproducibility and Evidence Control}
\label{sec:reproducibility}

The paper is generated from validator-backed evidence rather than copied from terminal summaries.
The TempGlitch follow-up validator checks required files, hashes, support equality across all 60
rows, calibration episode identities, leakage counts, and false locked-test flags. R5-XGame has
separate output and package-intake validators. Key commands and SHA256 identifiers are retained in
the research reports and summarized in Appendix~\ref{app:artifact-provenance}. K1, K2, K3, and the
qualitative timeline lane each add their own intake receipts and protocol-specific validators.

Paper-facing statements are registered before use. The repository claim registry identifies the
evidence source, status, intended manuscript location, and prohibited interpretation for each
claim. A paper claim map then translates those entries into allowed wording. The fast context cache
keeps the current gate, claim boundary, next action, and handoff synchronized for subsequent
agents.

Submission tables are regenerated from repository evidence with
\texttt{scripts/make\_paper\_tables.py}, which reads the TempGlitch follow-up metrics, K1 summary,
K2 intake summary, K3 controlled-ablation bundle, and qualitative timeline receipt. Generated
data, raw scores, checkpoints, and output directories remain outside Git; tracked documents
preserve hashes, support, commands, and exact summaries. Locked-test access remains independently
closed, and the local workspace still cannot claim an official LLNCS PDF build without the
external Springer class files and toolchain.
