\section{Limitations}
\label{sec:limitations}

All empirical evidence is non-locked and validation-only. The main TempGlitch follow-up has 12
normal-negative and 22 buggy-positive evaluation episodes, while its expanded K-A companion has 29
normal-negative and 38 buggy-positive evaluation episodes. Both use only two calibration-normal
episodes. Their AUROC confidence intervals are wide, the best LeWM and baseline intervals overlap,
and operating-point false-positive rates remain high. R5-XGame also has only 12 normal negatives,
is positive-heavy with 60 buggy positives, and exhibits seed sensitivity.

TempGlitch provides binary video-level labels rather than verified temporal spans, while the
current executable GlitchBench path is image-level and the current validated WOB/XGame artifacts
carry episode-level roles only. Window scores therefore cannot be interpreted as validated glitch
localization. Qualitative surprise timelines may illustrate score dynamics, but they do not
measure onset, offset, duration, or event-level recall.

K2 is a tiny synthetic-normal image-level split. Its negative comparison is informative, but it is
not the same task as episode-level gameplay QA on naturally occurring normal footage. K3 is a
mechanistic validation-normal training readout, not a binary glitch-detection benchmark. The two
TempGlitch and R5-XGame evidence families remain non-comparable because their support, calibration,
domain, action mode, and training lineage differ. R5-WOB has no normal-negative evaluation
episodes and remains positive-probe evidence only.

The study contains no locked-test result, no broad cross-game generalization result, no real-time
latency study, and no deployment trial. K3 also does not show a positive SIGReg or
action-conditioning readout for the specific validated artifact, so any broader claim in those
directions remains unsupported. The experiments in this paper were conducted on a single compute
platform (Kaggle T4\,$\times$\,2); latency, throughput, and scalability to larger video archives
are not evaluated.

The current results also do not include a full TimeSformer or fully fine-tuned VideoMAE anomaly
detector. The included VideoMAE-small feature-distance row is a bounded learned baseline on the
current support, but larger video transformers remain future work under a matched compute and
selection protocol.

Table~\ref{tab:limitations-claim-boundary} summarizes the principal limitations and their
implication for claim scope.

\input{tables/limitations_claim_boundary}
