\section{Conclusion}
\label{sec:conclusion}

This study presents a fuller but still bounded method-paper evaluation of a JEPA-style
latent-surprise detector for gameplay glitch detection. On the frozen pair-disjoint TempGlitch
follow-up, the best recorded LeWM row remains numerically above the simple baselines and the
exact-support learned baselines in observed AUROC. At the same time, the strongest learned-baseline
comparison is statistically inconclusive, the negative support and calibration support remain
small, and the operating-point false-positive rate is high.

The broader evidence lanes sharpen the method story rather than simply enlarging it. K2 provides a
bounded public-benchmark slice on which the current LeWM rows underperform validated simple and
learned-baseline rows. K3 provides a controlled mechanistic readout with no observed SIGReg
prediction-loss benefit and no stable real-action-over-zero-action gain. Qualitative timelines
improve interpretability but do not unlock temporal localization because span labels are absent.

The resulting contribution is an artifact-backed, leakage-aware detector evaluation with explicit
positive and negative findings. It does not establish broad superiority, cross-game
generalization, temporal localization, deployment readiness, or locked-test performance. Future
work has three natural extensions: expanding normal-episode coverage to improve calibration
robustness and reduce the current false-positive burden; adding verified temporal span
annotations so qualitative surprise timelines can become true localization metrics; and
evaluating larger video transformers under matched anomaly-detection protocols to test whether
JEPA-specific latent prediction offers advantages beyond architecture scale.
