\documentclass[10pt,conference]{IEEEtran}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{url}

\title{Latent World Models for Video Game Glitch Detection: A Leakage-Aware Evaluation Protocol}
\author{\IEEEauthorblockN{Anonymous for Review}}

\begin{document}
\maketitle

\begin{abstract}
We study whether latent world-model prediction errors can support video game glitch detection
under leakage-aware evaluation. The current manuscript scaffold documents the protocol, data
splits, safety gates, completed R5 episode-level evaluation provenance, and the remaining
pre-paper alignment work. It intentionally keeps placeholders for R3 archival clarification,
full paper-table insertion of the R5 family, ablations, and any conditional post-R5 World of
Bugs expansion. No locked-test result or broad performance conclusion is reported before the
required artifact-backed validation and claim review complete.
\end{abstract}

\section{Introduction}
Video game glitches are visually diverse, temporally sparse, and expensive to annotate. A
latent-surprise detector is attractive because glitches may violate learned normal gameplay
dynamics. This paper evaluates that hypothesis only through predeclared non-locked validation
experiments and strict artifact checks.

\section{Related Work}
We position the study against gameplay glitch benchmarks, video anomaly detection, latent world
models, and joint-embedding predictive architectures \cite{tempglitch,glitchbench,lewm,ijepa,vjepa}.

\section{Protocol}
The protocol trains or calibrates only on allowed train-normal data. Checkpoint selection and early
stopping use validation-normal prediction loss only. Validation-buggy episodes are reserved for
post-training evaluation. The locked test remains closed until a separate frozen validation
decision and explicit user command.

\section{Data}
The research MVP source contains train-normal, validation-normal, and validation-buggy TempGlitch
Lance datasets with frozen hashes recorded in the repository. R3 seed 42 uses only:
\begin{itemize}
  \item train-normal: \texttt{tempglitch\_train\_normal\_all\_local.lance}
  \item validation-normal: \texttt{tempglitch\_validation\_normal\_all\_local.lance}
\end{itemize}
No validation-buggy or locked-test path is used during training, fitting, checkpoint selection, or
early stopping.

\section{Method}
The LeWM path trains a JEPA-style latent world model on normal gameplay and later evaluates latent
prediction surprise at episode level. Baselines and ablations are predeclared in the roadmap, but
their results are not inserted until their artifacts validate. A World of Bugs cross-game,
real-action extension is planned only as a controlled post-R5 expansion track.

\section{R3 Seed 42 Training}
TODO_R3_SEED42_RESULT

\section{R4 Multi-Seed Training}
Artifact-backed R4 rerun archives for seeds 43 and 44 were locally SHA256-verified and both
per-seed artifact validators passed. Detection metrics remain pending until R5 identical-episode
evaluation.

\section{R5 Episode-Level Evaluation}
The repository now contains a completed provenance-bound non-locked TempGlitch R5
identical-episode bundle; see `docs/research/69_r5_tempglitch_identical_episode_results.md` for
the frozen manifest, score, metric, and provenance hashes plus the exact qualified result table.
Full paper-table integration remains pending in this scaffold.

\section{Ablations}
TODO_ABLATION_RESULT

\section{Limitations}
This scaffold makes no claim of state of the art, superiority over baselines, temporal
localization, SIGReg benefit, or locked-test performance. Negative or failed infrastructure results
remain part of the record.

\section{Conclusion}
The project now has artifact-backed R4 rerun training archives for seeds 43 and 44. Scientific
conclusions remain limited to the exact qualified non-locked TempGlitch R5 family now recorded in
the repository. Any World of Bugs expansion remains conditional on that TempGlitch R5 checkpoint,
separate planning approval, and continued locked-test closure.

\bibliographystyle{IEEEtran}
\bibliography{references}
\end{document}
